### 2021-01-24 paper/intro.tex
Fleshing out Sec 1.2

For example, we can recover the expected semantics
for the above example by choosing
the predicate transformer which is independent of $(\DR x0)$
but dependent on $(\DR y0)$, which is the transformer
which maps $\bForm$ to $(s{=}0) \limplies \bForm$.
  \begin{gather*}
    r\GETS x\SEMI s\GETS y\SEMI \IF{s{<}1} \THEN z\GETS r\&s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1ex and 1.5em]
        \event{rx0}{\DR{x}{0}}{}
        \event{ry0}{\DR{y}{0}}{right=of rx0}
        \event{wz0}{(s{=}0) \limplies (s {<} 1) \land (r\&s){=}0 \mid \DW{z}{0}}{right=of ry0}
        \xform{rx0ry0d}{(r{=}0) \limplies(s{=}0) \limplies \bForm}{below=of ry0}
        \xform{rx0d}{(r{=}0) \limplies \bForm}{above=of rx0}
        \xform{ry0d}{(s{=}0) \limplies \bForm}{right=of rx0d}
        \xform{wz0i}{\bForm}{above=of wz0}
        \po{ry0}{wz0}
        \xo{rx0}{rx0d}
        \xo{ry0}{ry0d}
        \xo{rx0}{rx0ry0d}
        \xo{ry0}{rx0ry0d}
      \end{tikzinline}}
  \end{gather*}

>>>>

For example, we can recover the expected semantics
for the above example by choosing
the predicate transformer which is independent of $(\DR x0)$
but dependent on $(\DR y0)$, which is the transformer
which maps $\bForm$ to $(s{=}0) \limplies \bForm$.
  \begin{gather*}
    r\GETS x\SEMI s\GETS y\SEMI \IF{s{<}1} \THEN z\GETS r\&s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1ex and 1.5em]
        \event{rx0}{\DR{x}{0}}{}
        \event{ry0}{\DR{y}{0}}{right=of rx0}
        \event{wz0}{(s{=}0) \limplies (s {<} 1) \land (r\&s){=}0 \mid \DW{z}{0}}{right=of ry0}
        \xform{rx0ry0d}{(r{=}0) \limplies(s{=}0) \limplies \bForm}{below=of ry0}
        \xform{rx0d}{(r{=}0) \limplies \bForm}{above=of rx0}
        \xform{ry0d}{(s{=}0) \limplies \bForm}{right=of rx0d}
        \xform{wz0i}{\bForm}{above=of wz0}
        \po{ry0}{wz0}
        \xo{rx0}{rx0d}
        \xo{ry0}{ry0d}
        \xo{rx0}{rx0ry0d}
        \xo{ry0}{rx0ry0d}
      \end{tikzinline}}
  \end{gather*}
As a sanity check, we can see that sequential composition is
associative in this case, since it does not matter whether we
associate to the left, with intermediate step:
  \begin{gather*}
    r\GETS x\SEMI s\GETS y
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1ex and 1.5em]
        \event{rx0}{\DR{x}{0}}{}
        \event{ry0}{\DR{y}{0}}{right=of rx0}
        \xform{rx0ry0d}{(r{=}0) \limplies(s{=}0) \limplies \bForm}{below=of ry0}
        \xform{rx0d}{(r{=}0) \limplies \bForm}{above=of rx0}
        \xform{ry0d}{(s{=}0) \limplies \bForm}{right=of rx0d}
        \xform{wz0i}{\bForm}{right=of ry0d}
        \xo{rx0}{rx0d}
        \xo{ry0}{ry0d}
        \xo{rx0}{rx0ry0d}
        \xo{ry0}{rx0ry0d}
      \end{tikzinline}}
  \end{gather*}
or to the right, with intermediate step:
    \begin{gather*}
    s\GETS y\SEMI \IF{s{<}1} \THEN z\GETS r\&s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1ex and 1.5em]
        \event{ry0}{\DR{y}{0}}{}
        \event{wz0}{(s{=}0) \limplies (s {<} 1) \land (r\&s){=}0 \mid \DW{z}{0}}{right=of ry0}
        \xform{ry0d}{(s{=}0) \limplies \bForm}{above=of ry0}
        \xform{wz0i}{\bForm}{above=of wz0}
        \po{ry0}{wz0}
        \xo{ry0}{ry0d}
      \end{tikzinline}}
  \end{gather*}
This is an instance of a general result that sequential composition forms a monoid,
as one would hope.
